An algorithm for finding the global extremum\\ of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-08-31 2023/MMST/samplepaper.tex
fix last picture (titles) + some titles in text

\begin{table}[h]
\caption{Comparison of the original and modified GSA}\label{tab1}
\centering
\begin{tabular}{|l|c|c|c|}
\hline
 &  { classical }  & { round district }  & { random district }  \\
\hline
Average number of trials & 781.7	& 854.9 & 839.0 \\
\begin{tabular}{@{}l@{}} {Average number of trials } \\  { in non-computability regions } \end{tabular}  & - & 185.8 & 42.3 \\
{Number of solved problems } & 100 / 100 & 100 / 100  &  100 / 100 \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Problem series of various dimensions}\label{tab2}
\centering
\begin{tabular}{|l|l|c|c|c|}
\hline
 N &  Task type & Average number of trials & \begin{tabular}{@{}c@{}} {Average number of trials} \\  {in non-computability regions} \end{tabular} & Solved problems \\
\hline
$3$ & original & 12251.1 & - & 100 / 100 \\
$ $ & round & 12201.8 & 4763.6 & 100 / 100 \\
$ $ & random & 12210.7 & 63.4 & 100 / 100 \\
\hline
$4$ & original & 25144.5 & - & 100 / 100 \\
$ $ & round & 29840.3 & 15004.4  & 100 / 100 \\
$ $ & random & 25287.5 & 26.4 & 100 / 100 \\
\hline
$5$ & original & 56725.9 & - & 100 / 100 \\
$ $ & round & 47840.1 & 24109.2 & 100 / 100\\
$ $ & random & 57874.8 & 82.6 & 100 / 100\\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h]
\caption{Comparison of the original and modified GSA}\label{tab1}
\centering
\begin{tabular}{|l|c|c|c|}
\hline
 &  { original }  & { round }  & { random }  \\
\hline
Average number of trials & 781.7	& 854.9 & 839.0 \\
\begin{tabular}{@{}l@{}} {Average number of trials } \\  { in non-computability regions } \end{tabular}  & - & 185.8 & 42.3 \\
{Number of solved problems } & 100 / 100 & 100 / 100  &  100 / 100 \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Problem series of various dimensions}\label{tab2}
\centering
\begin{tabular}{|l|l|c|c|c|}
\hline
 \begin{tabular}{@{}c@{}} {N} \\ {}\end{tabular} &
 \begin{tabular}{@{}c@{}} {Problem} \\ {type} \end{tabular} &
 \begin{tabular}{@{}c@{}} {Average number of trials} \\ {} \end{tabular} &
 \begin{tabular}{@{}c@{}} {Average number of trials} \\ {in non-computability regions} \end{tabular} &
 \begin{tabular}{@{}c@{}} {Solved problems} \\ {}\end{tabular} \\
\hline
$3$ & original & 12251.1 & - & 100 / 100 \\
$ $ & round & 12201.8 & 4763.6 & 100 / 100 \\
$ $ & random & 12210.7 & 63.4 & 100 / 100 \\
\hline
$4$ & original & 25144.5 & - & 100 / 100 \\
$ $ & round & 29840.3 & 15004.4  & 100 / 100 \\
$ $ & random & 25287.5 & 26.4 & 100 / 100 \\
\hline
$5$ & original & 56725.9 & - & 100 / 100 \\
$ $ & round & 47840.1 & 24109.2 & 100 / 100\\
$ $ & random & 57874.8 & 82.6 & 100 / 100\\
\hline
\end{tabular}
\end{table}
